\documentclass[a4paper,12pt,oneside]{book}%extreport
\usepackage{times} 
% \usepackage{multibib}
\usepackage{lipsum}
\usepackage{appendix}
\usepackage[shortlabels]{enumitem}
\usepackage{booktabs}
\usepackage{rotating} % Rotating table
\usepackage{hhline}
\usepackage{colortbl}
\usepackage{afterpage}
\usepackage{mathtools} %Fixes/improves amsmath
\usepackage{setspace}
\usepackage[utf8]{vietnam} 
\usepackage{amstext, amsmath,latexsym,amsbsy,amssymb, amssymb,amsthm,amsfonts,multicol, nccmath}
\usepackage[left=3cm,right=2cm,top=2.5cm,bottom=3cm,footskip=40pt]{geometry}
\usepackage{pdflscape}
\usepackage{apacite}
\usepackage{tikz}
\usepackage{array}
\newcolumntype{C}[1]{>{\centering\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\usetikzlibrary{calc}
\usepackage{tabularx}
\usepackage{multicol}
\usepackage{array,color,colortbl}
\setcounter{secnumdepth}{4}
 %\usepackage[square,numbers]{natbib}
\usepackage[square, comma, numbers, sort&compress]{natbib}
\setlength{\parindent}{1cm}
\usepackage{color}
\usepackage{indentfirst}
\usepackage{exscale,eucal}
\usepackage{fancyhdr}
\usepackage{fncychap}
\usepackage[chapter]{algorithm}
\usepackage{multirow}
\usepackage{graphicx}
\usepackage{algpseudocode}
\usepackage{tabularx,multicol,multirow,longtable}
\usepackage{etoolbox}
\usepackage{tikz}	\usetikzlibrary{calc,arrows,decorations.pathmorphing,backgrounds,positioning,fit,shapes,decorations.shapes, shapes.geometric, decorations.pathreplacing, decorations.text}
 
	\tikzstyle{block} = [draw,rectangle,thick,minimum height=2em,minimum width=2em,drop shadow,fill=blue!50]
	\tikzstyle{sum} = [draw,circle,inner sep=0mm,minimum size=2mm]
	\tikzstyle{connector} = [->,thick]
	\tikzstyle{line} = [very thick]
	\tikzstyle{branch} = [circle,inner sep=0pt,minimum size=1mm,fill=black,draw=black]
	\tikzstyle{axes} = [->,>=stealth',semithick]
	\tikzstyle{important line} = [very thick,draw=red]
	\tikzstyle{important text} = [rounded corners,fill=red!10,inner sep=1ex]
\usepackage{circuitikz}
\usepackage{pgfplots}
\pgfplotsset{compat=1.16}
\usepackage[numbers]{natbib}
\usepackage{titlesec}
\usepackage[labelsep=period]{caption}
\usepackage{subfigure}
\DeclareCaptionFormat{myformat}{\fontsize{13}{15}\selectfont#1#2#3}
\captionsetup{format=myformat}
\usepackage{titletoc}
\titlelabel{\thetitle.\,\,}
\titleformat{\chapter}[display] 
  {\fontsize{14}{16}\selectfont\bfseries\centering}
  {\MakeUppercase{\chaptertitlename}\ \thechapter}{0pt}{\fontsize{14}{16}\selectfont\MakeUppercase}
\titlespacing{\chapter}{0pt}{0pt}{40pt} 
\titleformat*{\section}{\fontsize{14}{14}\selectfont\bfseries}
\titleformat*{\subsection}{\fontsize{14}{14}\selectfont\bfseries\slshape}
\titleformat*{\subsubsection}{\fontsize{14}{14}\slshape}
\titleformat*{\paragraph}{\large\bfseries}
\titleformat*{\subparagraph}{\large\bfseries}
\graphicspath {{figures/}}

\titlespacing\section{0pt}{6pt plus 4pt minus 2pt}{1pt plus 2pt minus 2pt} 
\titlespacing\subsection{0pt}{6pt plus 4pt minus 2pt}{1pt plus 2pt minus 2pt}
\titlespacing\subsubsection{0pt}{6pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}
\titlespacing\subsubsubsection{0pt}{6pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}

\usepackage[subfigure]{tocloft} 

\cftsetpnumwidth{20pt}
\titlecontents{chapter}
  [0pt]
  {}
  {\fontsize{13.5}{14}\selectfont\MakeUppercase{\chaptername}\ \thecontentslabel.\,\,}
  {}
  {\cftdotfill{\cftdotsep}\contentspage} 
	\renewcommand{\cftsecaftersnum}{.}%
	\renewcommand{\cftsubsecaftersnum}{.}%

\usetikzlibrary{calc}
\newtheorem{definition}{\bf Định nghĩa}[chapter]
\newtheorem{theorem}{\bf Định lý}[chapter]
\newtheorem{lemma}{\bf Bổ đề}[chapter]

\renewcommand{\cftfigfont}{Hình~}
\renewcommand{\cfttabfont}{Bảng~ }
\floatname{algorithm}{Thuật toán}
\makeatletter
\renewcommand\@biblabel[1]{[#1]}
\renewcommand\harvardyearleft{\unskip~(}
\renewcommand\harvardyearright{\unskip )}
\makeatother
\renewcommand{\baselinestretch}{1.4}
\flushbottom
\renewcommand*{\bibfont}{\fontsize{13}{16}\selectfont}

\usepackage[hidelinks, unicode]{hyperref}

\begin{document}
\fontsize{13}{15.5}\selectfont

\pagestyle{empty}
\input{cover/Biangoai}
\newpage
\pagestyle{plain}
\pagenumbering{gobble}
\input{cover/Biatrong}
\newpage
\def\baselinestretch{1.3}
\pagestyle{plain}
\pagenumbering{gobble}
\input{cover/loicamdoan}
\newpage
\input{cover/loicamon} 
\newpage
\input{cover/tomtat}
\newpage
\pagenumbering{roman}


\setlength{\parindent}{1cm}
\setlength{\parskip}{0.6ex}

\fontsize{13}{16}\selectfont
\renewcommand{\contentsname}{\vspace{-70pt}\centerline{\fontsize{14}{16}\selectfont\MakeUppercase{Mục lục}}}
\clearpage
\phantomsection
\addcontentsline{toc}{chapter}{Mục lục}
\tableofcontents
\clearpage
\input{cover/tomtat}
\newpage
\clearpage
\phantomsection
\addcontentsline{toc}{chapter}{Danh mục hình vẽ}
\renewcommand{\listfigurename}{\vspace{-70pt}\centerline{\fontsize{14}{16}\selectfont{\MakeUppercase{Danh mục   hình vẽ}}}}
\listoffigures
\fontsize{13}{16}\selectfont
\newpage
\clearpage
\phantomsection
\addcontentsline{toc}{chapter}{Danh mục bảng biểu}
\renewcommand{\listtablename}{\vspace{-70pt}\centerline{\fontsize{14}{16}\selectfont{\MakeUppercase{Danh mục bảng biểu}}}}
\listoftables
\fontsize{13}{16}\selectfont
\newpage

\pagenumbering{arabic}
\pagestyle{plain}

\input{chapter/Chap0_Introduction}
\newpage
\input{chapter/Chap1_Background}
\newpage
\input{chapter/Chap2_GNUSDR}
\newpage
\input{chapter/Chap3_Main}
\newpage
\input{chapter/Chap4_Ketluan}
\newpage

\appendix
\input{cover/phuluc}
\def\baselinestretch{1}
\vspace{-2cm}
\renewcommand{\bibname}{Tài liệu tham khảo}
\clearpage
\phantomsection
\addcontentsline{toc}{chapter}{{TÀI LIỆU THAM KHẢO}}
\renewcommand{\refname}{Literary works}
\begin{thebibliography}{xx}
	\section*{Tiếng Việt}
	\vspace{0.3cm}
	\harvarditem{Quỳnh}{2015}{Quynh2015}
	Trần Thị Thúy Quỳnh , {\em {Nghi{\^{e}}n cứu
			n{\^{a}}ng cao hiệu năng của hệ t{\`{i}}m phương sử dụng anten
			kh{\^{o}}ng tầm pha trong m{\^{o}}i trường c{\'{a}}c nguồn t{\'{i}}n
			hiệu tương quan}}, Luận án tiến sĩ, 2015, tr.~19--23.
	\vspace{0.5cm}	
	\section*{Tiếng Anh}	
	
	\harvarditem{Feickert}{2005}{Feickert2005}
	Andrew Feickert, ``{The Joint Tactical
		Radio System (JTRS) and the Army{\'{s}} Future Combat System (FCS): Issues
		for Congress}'', {\em Congressional Research Service: Report}, 2005, pp.~1.
	
	\harvarditem[Bloessl et~al.]{Bloessl, Segata, Sommer \harvardand\
		Dressler}{2013}{Bloessl2013}
	B. Bloessl, M. Segata, C. Sommer \harvardand\ F. Dressler, ``An IEEE802.11a/g/p OFDM receiver for GNU radio'',
	{\em SRIF 2013 - Proceedings of the 2nd, 2013 ACM SIGCOMM Workshop on
	Software Radio Implementation Forum}, 2013, pp.~9--15.

	\harvarditem{BogdanDIA}{2015}{BogdanDIA2015}
	BogdanDIA  , ``{DVB-T implementation in gnuradio}'', 2015.
	\newline{[Online]. Available: $https://github.com/BogdanDIA/gr-dvbt$}

	\harvarditem[Bergstrom et~al.]{Bergstrom, Chuprun, Gifford \harvardand\
	Maalouli}{2002}{Bergstrom2002}
	C. Bergstrom, S. Chuprun, S. Gifford, \harvardand\ G. Maalouli
	, ``{Software defined radio (SDR)
	special military applications}'', {\em MILCOM 2002. Proceedings},
	{vol.~1}, 2002, pp.~383--388.
	
	\harvarditem{Bellini \harvardand\ Tosi}{1907}{Bellini1907}
	E. Bellini \harvardand\ A. Tosi,
	``{A directive system of wireless telegraphy}'', {\em Proceedings of the
		Physical Society of London}, vol.~21, no.~1, 1907, pp.~305--328.
	
	\harvarditem[Gomez-Miguelez et~al.]{Gomez-Miguelez, Garcia-Saavedra, Sutton,
		Serrano, Cano \harvardand\ Leith}{2016}{Gomez-Miguelez2016}
	I. Gomez-Miguelez, A. Garcia-Saavedra, Paul D. Sutton, P. Serrano, C. Cano
	\harvardand\ Douglas J. Leith,
	``{srsLTE: An open-source platform for LTE evolution and experimentation}'',
	{\em Proceedings of the Annual International Conference on Mobile Computing
		and Networking, MOBICOM}, 2016, pp.~25--32.
	
	\harvarditem{Ziskind \harvardand\ Wax}{1988}{Ziskind1988}
	I. Ziskind \harvardand\ M. Wax,
	``{Maximum Likelihood Localization of Multiple Sources by Alternating
		Projection}'', {\em IEEE Transactions on Acoustics, Speech, and Signal
		Processing}, {vol.~36}, no.~10, 1988, pp.~1553--1560.
	
	\harvarditem{Capon}{1969}{Capon2009}
	J. Capon, ``{High-resolution frequency-wavenumber spectrum analysis}'', 
	{\em Proceedings of the IEEE}, {vol.~57}, no.~8, 1969, pp.~1408--1418.
	
	\harvarditem{Liberti \harvardand\ Rappaport}{1999}{Liberti1999}
	Joseph C. Liberti \harvardand\ Theodore S. Rappaport, {\em Smart antennas for wireless communications: IS-95 and third generation CDMA applications}, 
	{Prentice Hall PTR}, 1999, pp.~134--134.
	
	\harvarditem{{Van Rijsbergen}}{n.d.}{VanRijsbergen}
	Kenneth van Rijsbergen, ``{The
		effectiveness of a homemade IMSI catcher build with YateBTS and a BladeRF}'', {\em Semanticscholar}, 2016.
	
	\harvarditem{{\em {KerberosSDR Demo software for direction finding and passive
				radar}}}{2019}{kerberos}
	{KerberosSDR: ``Demo software for direction finding and passive radar''}, 2019.
	\newline{[Online]. Available: $https://github.com/rtlsdrblog/kerberossdr$}
	
	\harvarditem{Nentwig}{2016}{Nentwig2016}
	M. Nentwig, ``{Delay estimation by FFT}'', {\em DSPRelated}, 2016.
	
	\harvarditem{{\em {DC offset and IQ Imbalance Correction {\textperiodcentered}
				Nuand/bladeRF Wiki}}}{n.d.}{Dccali}
	{ {Nuand/bladeRF, ``DC offset and IQ Imbalance Correction''.}} 
	\newline{[Online]. Available: $https://github.com/Nuand/bladeRF/wiki/DC-offset-and-IQ-Imbalance-Correction$}
	
	\harvarditem{{\em {Nuand: kalibrate-bladeRF}}}{2010}{kali}
	{Nuand/bladeRF: ``kalibrate-bladeRF''}, 2010.
	\newline{[Online]. Available: $https://github.com/Nuand/kalibrate-bladeRF$}
	
	\harvarditem[Kavitha et~al.]{Kavitha, {Meera Mohan}, Surya, Gandhiraj
		\harvardand\ Soman}{2015}{Kavitha2015}
	P. Kavitha, K. Meera Mohan, R. Surya, R. Gandhiraj \harvardand\ K.P. Soman, {``Implementation of CDMA in GNU radio''}, {\em Procedia Computer Science}, vol.~46, 2015, pp.~981--988.
	
	\harvarditem{Krysik}{2016}{multi-rtl}
	P. Krysik, ``{Multi-channel receiver with use of RTL-SDR dongles}'', 2016.
	\newline{[Online]. Available: $https://github.com/ptrkrysik/multi-rtl$}
	
	\harvarditem{Nehorai \harvardand\ A.}{1989}{Transactions1989}
	P. Stoica \harvardand\ A. Nehorai,
	``{MUSIC, Maximum Likelihood, and Cramer-Rao Bound}'', {\em IEEE Transactions
		on Acoustics, Speech, and Signal Processing}, {vol.~37}, no.~5, 1989.
	
	\harvarditem{{\em {PyBOMBS (Python Build Overlay Managed Bundle
				System)}}}{n.d.}{PyBombs}
	PyBOMBS: ``Python Build Overlay Managed Bundle System''.
	\newline{[Online]. Available: $https://github.com/gnuradio/pybombs$}
	
	\harvarditem{Bracewell}{1978}{Bracewell1978}
	Ronald N. Bracewell, {\em {The Fourier Transform and Its Applications}}, McGraw-Hill, 1978, pp.~46 and 243.
	
	\harvarditem{{R. I. Lackey and D. W. Upmal}}{1995}{Fakhrian2012}
	{R. I. Lackey and D. W. Upmal},
	``{Speakeasy: The Military Software Radio}'', {\em IEEE Communications
		Magazine}, {vol.~33}, no.~5, 1995, pp.~56--61.
	
	\harvarditem{Keen}{1922}{Darwin1895}
	R. Keen, {\em {Direction and Position Finding by Wireless}}, 1922.
	
	\harvarditem{Schmidt}{1986}{Schmidt2009a}
	R. Schmidt, ``{Multiple emitter
		location and signal parameter estimation}'', {\em IEEE Transactions on Antennas and Propagation}, vol.~34, no.~3, 1986, pp~276--280.
	
	\harvarditem[Whiting et~al.]{Whiting, Sorensen, Moon \harvardand\
		Gunther}{2018}{Whiting2018}
	S. Whiting, D. Sorensen, T. K. Moon \harvardand\ J. H. Gunther,
	 ``{Time and frequency corrections in
		a distributed radio network}'', {\em 2017 51st Asilomar Conference on Signals, Systems, and Computers}, 2017, pp.~1123--1126.
	
	\harvarditem{{Travis F Collins}}{n.d.}{TravisFCollins}
	 Srikanth Pagadarai, Travis Collins and Alexander M. Wyglinski, ``{Phase
		Synchronization Capability of TwinRX Daughterboards and DoA Estimation}'', {\em Ettus Research}, 2016, pp.~1--12.
	
\end{thebibliography}

\end{document}
